Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/tikz/results-flow.tex
Adding flow DAG of results

\documentclass[anon,12pt]{colt2021} % Anonymized submission
%\documentclass[final]{colt2020} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

% \documentclass{colt2020} % Include author names

% The following packages will be automatically loaded:
% amsmath, amssymb, natbib, graphicx, url, algorithm2e

\usepackage{times}

\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\PassOptionsToPackage{numbers, sort, compress}{natbib}

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{caption}
% NOTE: had to comment out "todo" in colt2021.cls
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usetikzlibrary{arrows}

\makeatletter
\let\Ginclude@graphics\@org@Ginclude@graphics 
\makeatother

%\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{orange!80!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\interior}{\mathrm{int}\,}
\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}

\newcommand{\range}{\mathrm{range}\,}
\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
\newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}

\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\cl}{\mathbf{cl}}
%\newcommand{\span}{\mathrm{span}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\im}{\mathrm{im}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\CVaR}{\mathrm{CVaR}}

\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{conjecture}{Conjecture}
%\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{condition}{Condition}
%\newtheorem{remark}{Remark}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}
\DeclareMathOperator*{\sgn}{sgn}

\usepackage{thmtools, thm-restate}
%\declaretheorem{corollary}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

%Indirect elicitation as a necessary condition for consistent surrogate losses
\title{Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates}

% Three or more authors with the same address:
\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
	\addr CU Boulder}

@@

\maketitle

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central\jessiet{a tad dramatic?} importance, we give a new technique for constructing lower bounds on the convex prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task. \jessiet{Not quite what we want to say- can someone refine this?}
%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.

For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.

%in a seemingly unrelated setting, finance problems blah blah.
In a seemingly unrelated problem, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
\jessie{Raf, helppp}

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings. 
Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).

\paragraph{The ``four quadrants'' of problem types}
Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
For further examples in quadrants 2 and 3, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}

\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
\jessiet{Make this subsection more concise?}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss~\citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).
\jessiet{Can trim this paragraph significantly}

\jessiet{This paragraph a little redundant}
The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
% This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g. Quadrants 1 and 3. 
%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}

\jessiet{Proposed paragraph about calibration to replace \S 2.2}
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

%\begin{figure}
%	\begin{minipage}{0.25\linewidth}
%	\caption{The four quadrants of prediction tasks; Theorem~\ref{thm:consistent-implies-indir-elic} allows us to understand the relationship between indirect elicitation and consistency in all four quadrants for the first time.}\label{fig:four-quadrants}	
%	\end{minipage}
%	\hfill
%	\begin{minipage}{0.72\linewidth}
%	\centering
%	\includegraphics[width=0.95\linewidth]{tikz/consistency-elicitation-calibration.pdf}
%	\end{minipage}
%\end{figure}

\begin{table}
	\begin{center}
	\begin{tabular}{|p{12ex}||l|l|} 
		\hline
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
		{\em prediction} & & \\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}
\begin{center}
\resizebox{0.7\linewidth}{!}{%
\begin{tikzpicture}

@@

%edges
\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
\draw[edge] (consis-gam) to node[above, sloped]{\footnotesize {Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}}} (conscvx-bd);
\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);

\end{tikzpicture}
}
\end{center}

\paragraph{Contributions}
\jessiet{Almost definitely want to re-format and polish this.}
Our contributions are as follows:
\begin{itemize}
	\item Formalize a notion of consistency with respect to a target statistic (Definition~\ref{def:consistent-prop}) and show its relationship to consistency with respect to a target loss (Lemma~\ref{lem:consistent-loss-implies-prop}).
	\item Show indirect elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
	\item Present a new framework for deriving lower bounds on the prediction dimension of consistent convex surrogates (Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}).
	These bounds are the first to our knowledge that can be applied in all four quadrants.
	\item Use this framework to derive new bounds for well-studied problems such as abstain loss (\S~\ref{sec:finite-calib}) and variance, entropy, and norms (\S~\ref{sec:contin-consis}).
\end{itemize}

\section{Preliminaries \jessie{Setting?}}\label{sec:related-work}

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with a convex set of distributions over outcomes $\P \subseteq \simplex$, through tools such as property elicitation.
When we have $p$ over outcomes $\Y$, we often write the expectation of a function $\E_{Y \sim p} L(\cdot,Y) := \E_p L(\cdot,Y)$.

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear. \jessie{Added line in prev. paragraph- feel free to burn if happy.}}
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.

% For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
% Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.

\subsection{Property elicitation}\label{subsec:properties}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
Intuitively, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set.
A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$\raft{added, since sec 6 gets confusing without this single-arrow notation}.
We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
Typically, we denote the target property by $\gamma$, and the surrogate by $\Gamma$.

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).

An important caveat to the above definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\raf{Check me!}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

% Property elicitation of a single property is well-understood~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \citet{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
% Additionally, \citet{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$. \jessiet{right?}
%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.

\subsection{Prediction dimension and elicitation complexity}\label{subsec:complexity}

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
In their setting (Quadrant 1), this is equivalent to convex consistency dimension (Definition~\ref{def:cvx-consistency-dim}).
Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

%\begin{definition}[Convex Calibration Dimension]
%	Given a target discrete loss $\ell$, its \emph{convex calibration dimension} $\ccdim(\ell)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
%	jessiet{Change this def to be about consistent prediction dimension}
%  \btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
%\end{definition}

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
A priori, this definition does not really make sense given a target statistic.
In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}

In the case of a target statistic $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.

>>>>

\documentclass[tikz]{standalone}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{import}
\usepackage{amsmath, amssymb, amsfonts}
\usetikzlibrary{calc}
\newcommand{\R}{\mathcal{R}}
\newcommand{\conscvx}{\mathrm{cons}_\mathrm{cvx}}

\usetikzlibrary{arrows}

@@

	\begin{tikzpicture}

@@

	%edges
	\draw[edge, <->] (consis-ell) to node[above]{Lemma~\ref{lem:consistent-loss-implies-prop}} (consis-gam);
	\draw[edge] (consis-gam) to node[above, sloped]{Theorem~\ref{thm:consistent-implies-indir-elic}} (indir-elic);
	\draw[edge] (indir-elic) to node[above, sloped]{Lemma~\ref{lem:convex-flats-inf-dim}} (d-flats);
	\draw[edge] (d-flats) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
	\draw[edge] (consis-gam) to node[above, sloped]{Cors.~\ref{cor:Pcodim-flat-single-val-prop}, \ref{cor:Pcodim-flat-elic-relint-prop}} (conscvx-bd);
	\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:finite-calib}} (q1-bounds);
	\draw[edge] (conscvx-bd) to node[above, sloped]{\S~\ref{sec:contin-consis}} (q4-bounds);

	\end{tikzpicture}

\end{document}
